\chapter{Functions}
A \textbf{function} is a set of statements that are executed together when the function is called. Every function has a name, which is used to call the respective function.

A C++ function has two parts:

\begin{itemize}
    \item Function declaration
    \item Function definition
\end{itemize}

The declaration includes the function’s name, return type, and any parameters.

The definition is the actual body of the function which executes when a function is called. The body of a function is typically enclosed in curly braces.

\noindent A function can look like the example below:  
\begin{verbatim}
#include<iostream>
void hello(); //Function Declaration 

int main(){
    hello(); //Function call
    // Prints Hello!
}
void hello(){ //Function Definition
    std::cout << "Hello!";
}
\end{verbatim}

\section{Parameters}
Function parameters are placeholders for values passed to the function. They act as variables inside a function.
They are placed in the parantheses in the function declaration, \verb!int add(int a, int b)!. 

Consider the example below: 
\begin{verbatim}
#include<iostream>
void print_int(int i);

int main(){
    print_int(10); //Passes the value of 10 to the parameter i
    //Prints 10
}
void print_int(int i){
    std::cout << i;
}
\end{verbatim}

\section{Return Values}
A function that returns a value must have a \verb!return! statement. The data type of the return value also must match the method’s declared return type.

On the other hand, a \verb!void! function (one that does not return anything) does not require a return statement.

Consider the example below: 
\begin{verbatim}
int add(int a, int b);

int main(){
   int sum = add(6, 8); // sum = 14
    
}
void add(int a, int b){
    return a+b;
}
\end{verbatim}

\section{Scope}
The scope is the region of code that can access or view a given element:

\begin{itemize}
    \item Variables defined in global scope are accessible throughout the program.
    \item Variables defined in a function have local scope and are only accessible inside the function.
\end{itemize}

\begin{verbatim}
#include <iostream>
 
void print();
 
int i = 10;       // global variable
 
int main() { 
  std::cout << i << "\n"; 
}
void print() { 
  int j = 0;      // local variable
  i = 20;
  std::cout << i << "\n"; 
  std::cout << j << "\n";
}
\end{verbatim}