\chapter{References and Pointers}
\section{Memory Address}
In C++, the memory address is the location in the memory of an object. It can be accessed with the "address of" operator, \verb!&!.

Given a variable \verb!random_var! the memory address can be retrieved 
by printing out \verb!&random_var!. It will return something like: \verb!0x7ffd7caa5b54!.

\section{Pointers}
In C++, a pointer variable stores the memory address of something else.  
It is created using the \verb!*! sign.  
Example: \verb!int* pointer = &gum; //Gets address of something like 0x3fed7c9a8b578!

\section{References} 
In C++, a reference variable is an alias for another object. It is created using the \verb!&! sign. Two things to note:

\begin{enumerate}
    \item Anything done to the reference also happens to the original.
    \item Aliases cannot be changed to alias something else.
\end{enumerate}

Example: \verb!int &a = b; //Now a shares the same address as b!
\newpage
\section{Pass-By-Reference}
In C++, pass-by-reference refers to passing parameters to a function by using references.  

It allows the ability to:  

\begin{itemize}
    \item Modify the value of the function arguments.
    \item Avoid making copies of a variable/object for performance reasons.
\end{itemize}

\begin{verbatim}
void swap_num(int &i, int &j) {
  int temp = i;
  i = j;
  j = temp;
}
 
int main() {
  int a = 100;
  int b = 200;
 
  swap_num(a, b);
 
  std::cout << "A is " << a << "\n"; //Prints 200
  std::cout << "B is " << b << "\n"; //Prints 100
}
\end{verbatim}

\section{const Reference}
In C++, pass-by-reference with \verb!const! can be used for a function where the parameter(s) won’t change inside the function.

This saves the computational cost of making a copy of the argument.
\begin{verbatim}
int triple(int const &i) {
 
  return i * 3;
 
}
\end{verbatim}

\section{Dereference}
In C++, a dereference reference operator, \verb!*!, can be used to obtain the value pointed to by a pointer variable.
\begin{verbatim}
int gum = 3;
 
// * on left side is a pointer
int* pointer = &gum;
 
// * on right side is a dereference of that pointer
int dereference = *pointer;
\end{verbatim}